\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Aiden}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Vigue}}}}} % Last name
	
	\vspace{6pt}
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{At}{12}{\href{mailto:aiden@vigue.me}{aiden@vigue.me}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://vigue.me}{vigue.me}}\\
	\icon{Github}{12}{\href{https://github.com/acvigue}{github.com/acvigue}}\\
	\icon{Linkedin}{12}{\href{http://linkedin.com/in/aidenvigue/}{linkedin.com/in/aidenvigue}}
\end{minipage}

\vspace{0.1cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Objective}

\begin{minipage}[t]{1\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	Creative, hard-working, and self-motivated computer science student anticipating graduation in 2027. Seeking an internship to apply and grow my experience in firmware development and software engineering to help solve issues in today's world.
\end{minipage}

\vspace{0.1cm}

\cvsect{Technical Expertise}

\begin{minipage}[t]{1\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\textbf{Computer Skills:} CAD/CAE, Docker, Virtualization, UNIX Systems Administation, AWS, Google Cloud\\
	\textbf{Languages:} C/C++, Java, NodeJS \& TypeScript, Shell, Python, Rust\\
	\textbf{Software Packages:} ESP-IDF, CMake, Altium Designer, Autodesk Inventor \& Fusion 360, Xcode, Nginx\\
	\textbf{Hardware:} ARM Cortex-M, Espressif ESP32, Silabs EFR32 \& EFM8, Microchip AVR\\
\end{minipage}

\vspace{0.1cm}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{Expected 2027}
		{Purdue University - BSc Computer Science / Certificate in Entrepreneurship}
		{West Lafayette, Indiana}
		{Currently pursuing a Bachelor of Science in Computer Science with a focus on embedded systems and a certificate in entrepreneurship.}
	\entry
		{2023}
		{Cave Spring High School}
		{Roanoke, Virginia}
		{Showcased strong dedication to both academics and practical skills through coursework and hands-on projects at the Burton Center for Engineering while simultaneously taking college-level courses at Virginia Western Community College.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{Jan. 2024 -- Present}
		{Intern - Software \& Hardware Development}
		{Levitree}
		{Streamlined, packaged, and containerized multiple microservices to control and monitor PLCs attached to a host processor. Used embedded Linux distributions to prepare a ML-based climate change mitigation system for production. }
	\entry
		{2022 -- Aug. 2023}
		{Sales Team Lead - Customer Service}
		{Kohl's}
		{Managed front-end operations, streamlined returns process, operated customer service desk, and facilitated effective communication between employees and management. Oversaw the consistent achievement of departmental sales targets.  \textbf{Associate of the Month - June 2023} }
\end{entrylist}

%---------
%   PROJECTS
%---------

\cvsect{Projects}

\begin{entrylist}
	\entry
		{2023}
		{Multiprotocol Smart Home Hub}
		{}
		{Designed a custom circuit board with an ESP32 and various Silicon Labs IoT radio modules to operate as a wirelessly-connected smart home hub. Included a Bosch BME680 for environmental sensing. Used Altium Designer and Fusion 360.}
		\entry
		{2021 -- 2022}
		{Kinetic Sand Coffee Table}
		{}
		{Modeled a polar-style robotic arm in Autodesk Inventor that moves a magnet around in a bed of sand while following a preprogrammed path. Programmed in C++, using ESP-IDF. Designed a responsive web interface in TypeScript and Vue 3 following the latest standards.}
\end{entrylist}

\vspace{0.3cm}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{1\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Awards}
	
	\textbf{Instructables Fusion 360 Contest - Grand Prize} -- 2023\\
	\textbf{Eagle Scout (Boy Scouts of America)} -- 2022\\
	\textbf{Instructables Lighting Challenge - 1\textsuperscript{st} Place} -- 2021\\
	\textbf{GE Lights For Life - 1\textsuperscript{st} Place} -- 2021\\
\end{minipage}

\vspace{\baselineskip}

%----------------------------------------------------------------------------------------

\end{document}
